---
title: "TidyTemplate"
date: 2020-08-31
output: html_output
---

# TidyTuesday

Join the R4DS Online Learning Community in the weekly #TidyTuesday event!
Every week we post a raw dataset, a chart or article related to that dataset, and ask you to explore the data.
While the dataset will be “tamed”, it will not always be tidy! As such you might need to apply various R for Data Science techniques to wrangle the data into a true tidy format.
The goal of TidyTuesday is to apply your R skills, get feedback, explore other’s work, and connect with the greater #RStats community!
As such we encourage everyone of all skills to participate!

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytuesdayR)
library(cowplot)
library(googleway)
library(ggrepel)
library(ggspatial)
library(libwgeom)
library(sf)
library(ggtext)
library(extrafont)
# font_import()
library(rnaturalearth)
library(rnaturalearthdata)
library(ggridges)
library(tvthemes)
theme_set(theme_bw())
```

# Load the weekly Data

Dowload the weekly data and make available in the `tt` object.

```{r Load}

tt <- tt_load("2020-09-01")

```


# Readme

Take a look at the readme for the weekly data to get insight on the dataset.
This includes a data dictionary, source, and a link to an article on the data.

```{r Readme, eval = interactive()}

tt

```


# Glimpse Data

Take an initial look at the format of the data available.

```{r Glimpse}

tt %>% 
  map(glimpse)

yields <- tt$key_crop_yields

yields %>% View()
```

# Wrangle

Explore the data and process it into a nice format for plotting! Access each dataset by name by using a dollarsign after the `tt` object and then the name of the data set.

```{r Wrangle}

world <- ne_countries(scale = "medium", returnclass = "sf", continent = c("south america", "north america"))

america <- world %>%
  select(name) %>%
  inner_join(yields, by = c("name" = "Entity")) %>%
  rename(
    "Rice" = "Rice (tonnes per hectare)",
    "Wheat" = "Wheat (tonnes per hectare)",
    "Soybeans" = "Soybeans (tonnes per hectare)",
    "Potatoes" = "Potatoes (tonnes per hectare)",
    "Beans" = "Beans (tonnes per hectare)",
    "Peas" = "Peas (tonnes per hectare)",
    "Cassava" = "Cassava (tonnes per hectare)",
    "Barley" = "Barley (tonnes per hectare)",
    "Barley" = "Barley (tonnes per hectare)",
    "Cocoa beans" = "Cocoa beans (tonnes per hectare)",
    "Bananas" = "Bananas (tonnes per hectare)",
    "Maize" = "Maize (tonnes per hectare)"
  ) %>%
  pivot_longer(cols = Wheat:Bananas,
               names_to = "Crop",
               values_to = "Yield")

# Can I create a variable meaning change in productivity?
america_trial <- america %>%
  select(-geometry) %>%
  mutate(Yield = ifelse(is.na(Yield), 0, Yield))

productivity <- america_trial %>%
  group_by(name, Crop) %>%
  mutate(previous= lag(Yield, 1),
         change = Yield - previous,
         change = ifelse(is.na(change), 0, change)) %>%
  select(-previous) %>%
  rename("country" = "name")


top_6 <- productivity %>%
  group_by(country) %>%
  filter(Crop %in% c("Wheat", "Maize", "Barley", "Rice", "Beans")) %>%
  summarise(productivity_change = sum(change)) %>%
  ungroup() %>%
  arrange(desc(productivity_change)) %>%
  slice_max(productivity_change, n = 6) %>%
  pull(country)

bottom_6 <- productivity %>%
  group_by(country) %>%
  filter(Crop %in% c("Wheat", "Maize", "Barley", "Rice", "Beans")) %>%
  summarise(productivity_change = sum(change)) %>%
  ungroup() %>%
  arrange(desc(productivity_change)) %>%
  slice_min(productivity_change, n = 6) %>%
  pull(country)

top_2018 <- productivity %>%
  group_by(country) %>%
  filter(Crop %in% c("Wheat", "Maize", "Barley", "Rice", "Beans")) %>%
  filter(Year == 2018) %>%
  summarise(Yield = sum(Yield)) %>%
  ungroup() %>%
  arrange(desc(Yield)) %>%
  slice_max(Yield, n = 6) %>%
  pull(country)

every_fifth_year <- productivity %>%
  mutate(lustro = case_when(
    Year > 1961 & Year <= 1965 ~ "1962-1965",
    Year > 1965 & Year <= 1970 ~ "1966-1970",
    Year > 1970 & Year <= 1975 ~ "1971-1975",
    Year > 1975 & Year <= 1980 ~ "1976-1980",
    Year > 1980 & Year <= 1985 ~ "1981-1985",
    Year > 1985 & Year <= 1990 ~ "1986-1990", 
    Year > 1990 & Year <= 1995 ~ "1991-1995",
    Year > 1995 & Year <= 2000 ~ "1996-2000",
    Year > 2000 & Year <= 2005 ~ "2001-2005",
    Year > 2005 & Year <= 2010 ~ "2006-2010",
    Year > 2010 & Year <= 2015 ~ "2011-2015",
    Year > 2015 ~ "2015 - 2018"
  )) %>%
  group_by(country, lustro, Crop) %>%
  summarise(productivity_change = sum(change)) %>%
  ungroup() %>%
  na.omit() 

cereal_top_countries <- every_fifth_year %>%
  filter(Crop %in% c("Wheat", "Maize", "Barley", "Rice", "Beans"),
         country %in% top_6) 

cereal_2018_countries <- every_fifth_year %>%
  filter(Crop %in% c("Wheat", "Maize", "Barley", "Rice", "Beans"),
         country %in% top_2018) 

(all_time_cereal <- productivity %>%
  group_by(country) %>%
  filter(Crop %in% c("Wheat", "Maize", "Barley", "Rice", "Beans")) %>%
  summarise(productivity_change = sum(change)))
```


# Visualize

Using your processed dataset, create your unique visualization.

```{r Visualize}
# Visualize how cereal productivity has changed in top 6 countries

cereal_top_countries %>%
  group_by(country, lustro) %>%
  summarise(productivity_change = sum(productivity_change)) %>%
  mutate(cumulative = cumsum(productivity_change)) %>%
  ggplot(aes(lustro, cumulative, group = country, color = country, fill = country)) +
  geom_point() +
  geom_line(alpha = 0.8, size = 1.5) +
  labs(title = "How has cereal productivity changed over time in the Americas", subtitle = "Top productivity-increasing countries", x = "", y = "Productivity change (tonnes per hectare)") +
  coord_flip()

# Visualize how cereal productivity has changed in top 2018 productive countries

top_plot <- cereal_2018_countries %>%
  group_by(country, lustro) %>%
  summarise(productivity_change = sum(productivity_change)) %>%
  mutate(cumulative = cumsum(productivity_change)) %>%
  rename("Country" = "country") %>%
  ggplot(aes(lustro, cumulative, group = Country, color = Country, fill = Country)) +
  geom_point() +
  geom_line(alpha = 0.8, size = 1.5) +
  labs(title = "How has cereal productivity changed over time in the Americas:", subtitle = "Top productive countries (Corn, wheat, rice, beans and barley)", x = "", y = "Cumulative change in productivity (tonnes per hectare)") +
  coord_flip() +
  scale_color_avatar("FireNation") +
  theme(
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(color = "gray68"),
    axis.text = element_text(family = "Purisa", size = 12),
    axis.title = element_text(family = "Purisa", size = 13),
    legend.title = element_text(family = "Purisa", size = 12),
    legend.text = element_text(family = "Purisa", size = 9),
    plot.title = element_text(family = "Purisa", size = 20),
    plot.subtitle = element_text(family = "Purisa", size = 14),
    plot.background = element_rect(fill = "#caaf98", linetype = 0),
    legend.background = element_rect(fill = "#caaf98", linetype = 0),
    legend.box.background = element_blank(),
    legend.key = element_rect(fill = "#f4e3d2"),
    panel.background = element_rect(fill = "#f4e3d2")
    )
  

top_plot

# Visualize how cereal productivity has changed in America

map_plot <- all_time_cereal %>%
  inner_join(world, by = c("country" = "name")) %>%
  ggplot(aes(geometry = geometry)) +
  geom_sf(aes(fill = productivity_change)) +
  coord_sf(xlim = c(-170, -40), ylim = c(-55, 75)) +
  scale_fill_gradient2(
  low = "steelblue",
  mid = "#e2d13e",
  high = "darkred",
  midpoint = 12,
  na.value = "gray"
) + 
  guides(fill = guide_colorbar(title.position = "top")) +
  labs(fill = "Total change in cereal productivity (Tonnes per hectare)", caption = "#TidyTuesday | Source: Our World in Data | Graphic: Eliseo Dominguez - @elidomx") +
  theme_void() +
  theme(
    legend.position = "bottom",
    legend.key.width = unit(2.5, "cm"),
    legend.title = element_text(element_text(family = "Purisa", size = 20)),
    legend.text = element_text(family = "Purisa", size = 10),
    plot.caption = element_text(family = "Purisa", size = 7, hjust = 0.7, vjust = -10.2)
  )
  
map_plot

plot_grid(top_plot, map_plot, ncol = 2) +
  theme(
    plot.background = element_rect(fill = "#caaf98")
  )

```

### Now let's produce banana

```{r Wrangle}


top_6 <- productivity %>%
  group_by(country) %>%
  filter(Crop == "Bananas") %>%
  summarise(productivity_change = sum(change)) %>%
  ungroup() %>%
  arrange(desc(productivity_change)) %>%
  slice_max(productivity_change, n = 6) %>%
  pull(country)


top_2018 <- productivity %>%
  group_by(country) %>%
  filter(Crop == "Bananas") %>%
  filter(Year == 2018) %>%
  summarise(Yield = sum(Yield)) %>%
  ungroup() %>%
  arrange(desc(Yield)) %>%
  slice_max(Yield, n = 6) %>%
  pull(country)

bananas_2018_countries <- every_fifth_year %>%
  filter(Crop == "Bananas",
         country %in% top_2018) 

(all_time_bananas <- productivity %>%
  group_by(country) %>%
  filter(Crop == "Bananas") %>%
  summarise(productivity_change = sum(change)))
```

```{r Visualize}
# Visualize how cereal productivity has changed in top 2018 productive countries


top_plot <- bananas_2018_countries %>%
  group_by(country, lustro) %>%
  summarise(productivity_change = sum(productivity_change)) %>%
  mutate(cumulative = cumsum(productivity_change)) %>%
  rename("Country" = "country") %>%
  ggplot(aes(lustro, cumulative, group = Country, color = Country, fill = Country)) +
  geom_point() +
  geom_line(alpha = 0.8, size = 1.5) +
  labs(title = "How has bananas productivity changed over time in the Americas:", subtitle = "Top productive countries", x = "", y = "Cumulative change in productivity (tonnes per hectare)") +
  coord_flip() +
  scale_color_bigHero6() +
  theme(
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(color = "gray68"),
    axis.text = element_text(family = "Purisa", size = 12),
    axis.title = element_text(family = "Purisa", size = 13),
    legend.title = element_text(family = "Purisa", size = 12),
    legend.text = element_text(family = "Purisa", size = 9),
    plot.title = element_text(family = "Purisa", size = 20),
    plot.subtitle = element_text(family = "Purisa", size = 14),
    plot.background = element_rect(fill = "#eab201", linetype = 0),
    legend.background = element_rect(fill = "#eab201", linetype = 0),
    legend.box.background = element_blank(),
    legend.key = element_rect(fill = "#f4e3d2"),
    panel.background = element_rect(fill = "#f4e3d2")
    )
  

top_plot

# Visualize how cereal productivity has changed in America

# pal <- wesanderson::wes_palette("Darjeeling2", n = 3, type = "continuous")
pal <- wesanderson::wes_palette("Zissou1", n = 3, type = "continuous")

map_plot <- all_time_bananas %>%
  inner_join(world, by = c("country" = "name")) %>%
  ggplot(aes(geometry = geometry)) +
  geom_sf(aes(fill = productivity_change)) +
  coord_sf(xlim = c(-170, -40), ylim = c(-55, 75)) +
  scale_fill_gradientn(colors = pal) + 
  guides(fill = guide_colorbar(title.position = "top")) +
  labs(fill = "Total change in bananas productivity (Tonnes per hectare)", caption = "#TidyTuesday | Source: Our World in Data | Graphic: Eliseo Dominguez - @elidomx") +
  theme_void() +
  theme(
    legend.position = "bottom",
    legend.key.width = unit(2.5, "cm"),
    legend.title = element_text(element_text(family = "Purisa", size = 20)),
    legend.text = element_text(family = "Purisa", size = 10),
    plot.caption = element_text(family = "Purisa", size = 7, hjust = 0.7, vjust = -10.2)
  )
  
map_plot

plot_grid(top_plot, map_plot, ncol = 2) +
  theme(
    plot.background = element_rect(fill = "#eab201")
  )

```



# Save Image

Save your image for sharing. Be sure to use the `#TidyTuesday` hashtag in your post on twitter! 

```{r}

# This will save your most recent plot
ggsave(
  filename = "My TidyTuesday Plot.png",
  device = "png")

```



misc
```{r}
productivity %>%
  filter(Crop %in% c("Wheat", "Maize", "Barley", "Rice", "Beans")) %>%
  group_by(country, Year) %>%
  filter(country == "Chile")
  mutate(productivity_change = sum(change)) %>%
  ungroup() %>%
  na.omit() %>%
  group_by(country, Year) %>%
  summarise(productivity_change = sum(productivity_change)) %>%
  mutate(cumulative = cumsum(productivity_change)) %>% View()


cereal_top_countries %>%
  group_by(country, lustro) %>%
  summarise(productivity_change = sum(productivity_change)) %>%
  mutate(cumulative = cumsum(productivity_change)) %>%
  View()
```

