---
title: "TidyTemplate"
date: 2020-09-21
output: html_output
---

# TidyTuesday

Join the R4DS Online Learning Community in the weekly #TidyTuesday event!
Every week we post a raw dataset, a chart or article related to that dataset, and ask you to explore the data.
While the dataset will be “tamed”, it will not always be tidy! As such you might need to apply various R for Data Science techniques to wrangle the data into a true tidy format.
The goal of TidyTuesday is to apply your R skills, get feedback, explore other’s work, and connect with the greater #RStats community!
As such we encourage everyone of all skills to participate!

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytuesdayR)
library(ggthemes)
library(fishualize)
library(scales)
library(extrafont)
library(cowplot)
```

# Load the weekly Data

Dowload the weekly data and make available in the `tt` object.

```{r Load}

tt <- tt_load("2020-09-22")

```


# Readme

Take a look at the readme for the weekly data to get insight on the dataset.
This includes a data dictionary, source, and a link to an article on the data.

```{r Readme, eval = interactive()}

tt

```


# Glimpse Data

Take an initial look at the format of the data available.

```{r Glimpse}

tt %>% 
  map(glimpse)

```

# Wrangle

Explore the data and process it into a nice format for plotting! Access each dataset by name by using a dollarsign after the `tt` object and then the name of the data set.

```{r Wrangle}
# Expedition Durations
head(exped$basecamp_date)
head(exped$termination_date)

exped_dur <- exped %>%
  filter(!is.na(termination_date)) %>%
  mutate(duration = termination_date - basecamp_date) %>%
  arrange(desc(duration)) 
  

# Deaths
dead <- tt$members %>%
  filter(died == TRUE) 
  
# Top 5 nationalities of the dead
top_dead <- dead %>%
  filter(year >= 1950,
         hired = TRUE) %>%
  group_by(citizenship) %>%
  count(sort = TRUE) %>%
  ungroup() %>%
  slice_head(n = 5) %>%
  pull(citizenship)

```


# Visualize

Using your processed dataset, create your unique visualization.

```{r Visualize}
theme_set(theme_light())


# duration of expeditions
plot_1 <- exped_dur %>%
  filter(termination_reason == "Success (main peak)") %>%
  na.omit() %>%
  mutate(peak_name = fct_lump_n(peak_name, 1)) %>%
  ggplot(aes(duration, fill = peak_name)) +
  geom_density(color = "#1b232b") +
  scale_fill_manual(values = c("#fffafa", "#816060")) +
  scale_y_continuous(labels = label_percent(accuracy = 1)) +
  labs(x = "Duration (days)", y = "", fill = "Peak", title = "Duration of expeditions to the Himalayan peaks", subtitle = "The Everest vs. other peaks", caption = "#TidyTuesday | Source: The Himalayan Database | Graphic: @elidomx") +
  theme(
    panel.background = element_rect(fill = "#668eab", linetype = 0),
    panel.border = element_blank(),
    plot.background = element_rect(fill = "#668eab", linetype = 0),
    panel.grid = element_blank(),
    axis.line = element_line(color = "#1b232b", size = 1),
    axis.ticks = element_line(color = "#1b232b", size = 1),
    axis.text = element_text(color = "#1b232b", size = 12, family = "Tibetan Machine Uni"),
    axis.title = element_text(color = "#1b232b", size = 13, family = "Tibetan Machine Uni"),
    plot.title = element_text(size = 26, family = "Tibetan Machine Uni", color = "#1b232b", face = "bold"),
    plot.subtitle = element_text(size = 19, family = "Tibetan Machine Uni", color = "#1b232b"),
    legend.background = element_blank(),
    legend.text = element_text(size = 12, family = "Tibetan Machine Uni", color = "#1b232b"),
    legend.title = element_text(size = 14, family = "Tibetan Machine Uni", color = "#1b232b"),
    plot.caption = element_text(family = "Tibetan Machine Uni", color = "#1b232b", hjust = 1.13)
  ) 

plot_1

ggdraw() +
  draw_plot(plot_1) +
  draw_label(label = "Pemba Dorje Sherpa",
             fontfamily = "Tibetan Machine Uni",
             size = 22,
             color = "#fffafa",
             x = 0.6,
             y = 0.78) +
  draw_label(label = "holds the record for the fastest ever
ascent to the summit of Mt Everest:",
             fontfamily = "Tibetan Machine Uni",
             size = 18,
             color = "#1b232b",
             x = 0.6,
             y = 0.715,
             hjust = 0.34) +
  draw_label(label = "8 hr 10 min",
             fontfamily = "Tibetan Machine Uni",
             size = 26,
             color = "#fffafa",
             fontface = "bold",
             x = 0.6217,
             y = 0.65,
             hjust = 0.77)



# Deaths:
# Hired vs. non-hired deaths
posn_j <- position_jitter(width = 0.2)
dead %>%
  filter(year >= 1950) %>%
  ggplot(aes(year, death_height_metres, color = hired)) +
  geom_point(position = posn_j, alpha = 0.7)



# Interesting:
dead %>%
  filter(year >= 1950) %>%
  mutate(citizenship = factor(citizenship),
         citizenship = fct_lump_n(citizenship, 2)) %>%
  ggplot(aes(year, death_height_metres, color = citizenship)) +
  geom_point(position = posn_jd, alpha = 0.7) +
  scale_color_manual(values = c("green", "red", "gray80")) +
  ylab("Height of death") +
  xlab("Year")


# Not used:
exped_dur %>%
  filter(termination_reason == "Success (main peak)") %>%
  na.omit() %>%
  mutate(peak_name = fct_lump_n(peak_name, 1)) %>%
  ggplot(aes(duration)) +
  geom_bar(stat = "bin", aes(y = ..density.., fill = peak_name)) +
  scale_fill_manual(values = c("#fffafa", "#9b7653")) +
  theme(
    panel.background = element_rect(fill = "#87ceeb")
  ) +
  geom_density(group = peak_name)

```

# Save Image

Save your image for sharing. Be sure to use the `#TidyTuesday` hashtag in your post on twitter! 

```{r}

# This will save your most recent plot
ggsave(
  filename = "My TidyTuesday Plot.png",
  device = "png")

```
